HyperLogLog: Exponentially Bad in Adversarial Settings

### 2020-04-28 docs/HLL_exp_bad/main.tex
ref

\subsection{Experimental Results}
Many different implementations of HLL are available online. Among the repositories collecting more than 350 stars on GitHub, we can cite \cite{clahll} and \cite{datasketch}. HLL is also featured in many frameworks, including Redis \cite{redis}, Google's BigQuery \cite{bigquery} and several products of Apache such as Spark \cite{spahll,spahll2} and Druid \cite{druhll}. It is interesting to point out that all these implementations use a constant number of buckets and a fixed hash function. Thus they are vulnerable to our attacks in scenarios S2 and S4.

@@

To assess the efficiency of our attacks, we can compare our results from Table~\ref{table:tab2} with the attack presented in Section 5.1 of~\cite{hllvuln}. In that paper, the authors target the Redis~\cite{redishll} open-source implementation of HLL and perform the attack against an empty sketch. Given a set of 250,000 items, the adversary could choose ``74,390 distinct items and obtain an HLL estimate of only 15,780``~\cite{hllvuln}, achieving a five-fold reduction from the true cardinality. In comparison, the adversary following our strategy is able to add 125,000 distinct items while keeping the cardinality estimate at 367, providing a reduction by a factor of 340 instead of 5. \kenny{I think we can say more here -- isn't it true that the attack in Section 5.1 of~\cite{hllvuln} is in the M2 scenario? Which is our S1? Whereas the attack you describe here is more like an S2 attack, a much weaker attack model?}

>>>>

\subsection{Experimental Results}
Many different implementations of HLL are available online. Among the repositories collecting more than 350 stars on GitHub, we can cite \cite{clahll} and \cite{datasketch}. HLL is also featured in many frameworks, including Redis \cite{redis}, Google's BigQuery \cite{bigquery}, Facebook's Airlift \cite{airlift} and several products of Apache such as Spark \cite{spahll} and Druid \cite{druhll}. It is interesting to point out that all these implementations use a constant number of buckets and a fixed hash function. Thus they are vulnerable to our attacks in scenarios S2 and S4.

@@

To assess the efficiency of our attacks, we can compare our results from Table~\ref{table:tab2} with the attack presented in Section 5.1 of~\cite{hllvuln}. In that paper, the authors target the Redis~\cite{redis} open-source implementation of HLL and perform the attack against an empty sketch. Given a set of 250,000 items, the adversary could choose ``74,390 distinct items and obtain an HLL estimate of only 15,780``~\cite{hllvuln}, achieving a five-fold reduction from the true cardinality. In comparison, the adversary following our strategy is able to add 125,000 distinct items while keeping the cardinality estimate at 367, providing a reduction by a factor of 340 instead of 5. \kenny{I think we can say more here -- isn't it true that the attack in Section 5.1 of~\cite{hllvuln} is in the M2 scenario? Which is our S1? Whereas the attack you describe here is more like an S2 attack, a much weaker attack model?}
